\pdfoutput=1 
\documentclass[a4paper,12pt]{article}

\usepackage{graphicx}% Include figure files



\graphicspath{{./Figures/}}
% packages
\usepackage{comment}
\usepackage{amsfonts}
\usepackage[dvipsnames]{xcolor}
\usepackage{placeins}
\usepackage[perpage]{footmisc}
\usepackage[normalem]{ulem}
\usepackage{caption}
\usepackage{makecell}
\usepackage{subcaption}
%\usepackage{subfig}
\usepackage{jinstpub} 
\usepackage{multicol,tabularx,capt-of}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{xfrac}
\usepackage{url}
\usepackage{soul}
\usepackage{hyperref}
\usepackage{chemformula}

\usepackage[binary-units,separate-uncertainty=true]{siunitx}
\usepackage{mathtools} 
%\usepackage{amssymb}
\usepackage{physics}
\usepackage[colorinlistoftodos, textsize=tiny, obeyFinal]{todonotes}





\title{ A Robust High Voltage Feedthrough for Cryogenic Detector Systems}

\author[a,1]{J.Doe,\note{Corresponding author}}


\affiliation[a]{SLAC National Accelerator Laboratory,\\ Sand Hill Rd. Menlo Park, Ca, 94025, USA}
\affiliation[b]{Michigan State University,\\ 426 Auditorium Rd. East Lansing, Mi, 48824, USA}


\abstract{
The need for reliable HV delivery into cryogenic environments
Key challenges: thermal contraction, dielectric integrity, long-term stability.
Summary of design.
Validation results: cryogenic cycling, mechanical compliance, HIPOT
Statement of broader applicability beyond LArTPCs} 



\keywords{cryogenic detectors}

\begin{document}
\listoftodos
\maketitle


\section{Introduction}
\label{sec:intro}

Frame the problem generically, not as DUNE-specific.

Content:
Role of HV feedthroughs in cryogenic systems (detectors, HV test stands, industrial cryo systems).
Key failure modes: dielectric breakdown at interfaces, thermal stress and cracking, differential contraction, surface flashover in gas ullage.
Limitations of existing approaches: ceramic FT, epoxy potting, rigid designs.

Positioning statement:
Introduce design as a mechanically compliant, cryogenically robust HVFT architecture.

Figures:
Conceptual diagram of HV feedthrough challenges (thermal gradients, interfaces, field regions)


\section{Design Requirements and Constraints}
\label{sec:req}

Keep this general but grounded in real constraints.

Content:
Electrical: operating voltage range, safety margin (HIPOT target), field grading requirements.
Mechanical: differential contraction (room temp → cryogenic), tolerance to thermal gradients.
Materials: dielectric compatibility, cryogenic stability, purity considerations (outgassing).
Integration: interface to HV cable, interface to cathode or load, sealing at flange.

Quietly inherit values from ND-LAr or FNAL requirements doc, but present them as representative design targets, not experiment requirements.

Figures:
Maybe a table summarizing requirements

\section{Feedthrough Design}
\label{sec:des}

\subsection{Overall Architecture}
Coaxial or quasi-coaxial structure
Insulation strategy (solid dielectric vs composite)
Field shaping approach (pill, surface disruptors, sock roll)

Figures:
Annotated full assembly cross-section(s)

\subsection{Electrical Design}
Field distribution strategy
Avoidance of high-field regions at interfaces (radii)
Grading (geometric, resistive, or both if applicable)

Figures:
Electrostatic simulation plots:field magnitude along axis, surface field at critical interfaces. \todo{James ask Marco}

\subsection{Mechanical Design and Compliance}
This is where the design differentiates itself.

Handling of thermal contraction: compliant regions, sliding or flexure interfaces.
Accommodation of thermal gradients.
Mechanical decoupling between cryostat boundary and cathode.

Explicitly mention: sufficient extension in the cathode connection to accommodate contraction.

Figures:
CAD showing compliant features
Thermal contraction schematic (room temp vs cryo)

\subsection{Materials and Interfaces}
Dielectric material choice
Conductor materials
Sealing approach (Ultra torr + CF)
Interface treatments (surface finish, stress relief)

Figures:
Exploded view of components
Interface detail close-ups

\subsection{Integration with System}
Keep this generic (not DUNE-specific)

Connection to HV supply (splice)
Connection to load (e.g. cathode)
Installation considerations

\section{Fabrication & Assembly}
\label{sec:fab}
Manufacturing approach (machining, bonding, assembly sequence)
Critical tolerances
Quality control steps

Figures:
Assembly sequence diagram
Photograph of fabricated unit

\section{Experimental Validation}
\label{sec:val}
This section must be rigorous and decisive.

\subsection{Cryogenic Testing}
Cooling profile
Number of cycles
Observations: no cracking, stable operation, no discharge

Explicitly mention: rapid cooling tolerance, stability under thermal gradients.

Figures:
Test setup photo
Temperature vs time plot

\subsection{Mechanical Performance}
Evidence of contraction accommodation
Cathode connection compliance

Figures:
Before/after geometry or displacement illustration

\subsection{High Potential Testing (HIPOT)}
Test configuration
Voltage levels reached
Duration
Margin relative to operating voltage

Figures:
HV test setup
current and voltage 

\section{Discussion}
\label{sec:dis}
Why the design works: field control + mechanical compliance. 
Comparison to traditional designs: rigid ceramic feedthroughs, epoxy-potted designs.
Reliability considerations: long-term stability, scalability.
Generalization: applicability to other cryogenic detectors, relevance to non-detector cryogenic HV systems

\section{Conclusions}
\label{sec:con}
Must be concise

Restate what was demonstrated: robust HV delivery, cryogenic stability, mechanical compliance.
Emphasize: validated design, transferable architecture.


\section{Acknowledgment} 


\clearpage

\bibliographystyle{JHEP}
\bibliography{HVFTBib}

\end{document}